|

### 2020-04-27 paper/Manuscript.Rmd
Correct spelling for RStudio

abstract: |
  The social sciences are amidst a paradigm shift towards open science. In part,
  this transition has been fueled by cases of scientific fraud and increasing
  awareness of questionable research practices and failed replications. However,
  open science is not
  merely a cure (or punishment) for this crisis - it is also an opportunity.
  Technological advances enable researchers to more easily conduct reliable,
  cumulative, collaborative science. Capitalizing on these advances has the
  potential to accelerate scientific progress. This tutorial paper introduces a
  workflow for open reproducible code in science (WORCS). WORCS is a 
  step-by-step procedure that researchers can follow to make an entire project
  Open and Reproducible. It is based on best practices, and can be used either
  in parallel to, or in absence of, top-down requirements by journals. WORCS
  lowers the threshold for adopting an open science workflow by providing this
  tutorial, along with an R-package with user-friendly support functions, and an
  Rstudio project template.

@@

This paper introduces WORCS: A Workflow for Open Reproducible Code in Science. WORCS is a lightweight approach to open science and computational reproducibility. It provides a step-by-step procedure that researchers can follow to make an entire research project Open and Reproducible. WORCS is based on best practices, and can be used either in parallel to, or in absence of, top-down requirements by journals. The main goal of WORCS is to lower the threshold for adopting an open science workflow by providing the present tutorial, along with an R-package with user-friendly support functions, and an Rstudio project template.

@@

A recently developed package strikes a great balance between user-friendliness and effectiveness: `renv`, developed by the team behind Rstudio. This package maintains a text-based log file of which packages are used, in what versions, and where they were installed from (e.g., CRAN, Bioconductor, GitHub). Being text-based, this log can be version controlled with Git. On a local computer, `renv` installs all packages used in a cache that is shared between all projects that use `renv`. Thus, if one of your projects uses a version of a package that is already in the cache, it does not need to be installed again. This overcomes the limitations of long installation times and large space requirements of `renv`. When someone else loads your project, `renv` will install all of the required packages onto a cache on their computer. Whereas `packrat` copies the source code of all packages, `renv` obtains the packages from their original repositories. Thus, as long as these repositories used maintain their archives, this solution is very lightweight and effective. It is not foolproof, but some have argued that all solutions for computational reproducibility have a limited shelf life [@brownHowLearnedStop2017]. Ultimately, the best solution might be to use a good-enough solution, like `renv`, and acknowledge that all code requires some maintenance if you want to reproduce it in the future.

@@

Working with R is simplified immensely by using the Rstudio user interface for R. Many of the tools used in WORCS are embedded directly into the visual user interface of Rstudio. Rstudio automates and streamlines many tedious or complicated aspects of working with R, Rmarkdown, and Git/GitHub. This makes Rstudio a comprehensive solution for open science research projects. Another important feature of Rstudio is project management. A project bundles writing, analyses, data, references, etcetera, into a self-contained folder, that can be uploaded entirely to GitHub and downloaded by future users. The `worcs` R-package installs a new Rstudio project template. When a new project is initialized from this template, much of the bookkeeping required to set up an open science project is performed automatically.

@@

When using R, software (R packages) can be conveniently cited by calling `citation("packagename")`. This returns an APA-style reference, and a BibTeX entry. However, users of the WORCS project template for Rstudio do not need to manually cite R-packages. WORCS generates a template manuscript in APA6 style, based on the `papaja` package [@austPapajaPrepareReproducible2020], which automatically cites all packages used.

@@

Aside from analysis code, the TOP-guidelines also encourage sharing new research materials, and details of the study design and analysis. These goals can be accomplished simply by placing any relevant documents in the Rstudio project folder, committing them to the Git repository, and pushing to GitHub. As with any document version controlled in this way, it is advisable to use plain text only.

@@

Several excellent preregistration templates are available in the R-package `prereg` [@austPreregMarkdownTemplates2019], including templates from organizations like [AsPredicted.org](AsPredicted.org) and [OSF.io](OSF.io), and from researchers [e.g., @vantveerPreregistrationSocialPsychology2016]. When opening a new Rstudio project with the WORCS project template, it is possible to select one of these preregistration templates, which will generate a file called `preregistration.Rmd`. This file should be used to document study plans, ideally prior to data collection.

@@

1. Create a new Private repository on github, and copy the repository link to the clipboard. The link will look like https://github.com/yourname/yourrepo.git
2. In Rstudio, click File > New Project > New directory > WORCS Project Template
    a. Paste the GitHub Repository address in the textbox
    b. Keep the checkbox for `renv` checked if you want to document all dependencies (recommended). The only reason not to do this is if you have dependencies outside of the R environment, or if you are using a more comprehensive solution for computational reproducibility, e.g., @peikertReproducibleDataAnalysis2019.
    c. Select a preregistration template
    d. Click Open in new session, and Create project
3. Write the preregistration `preregistration.Rmd`
4. In the top-right corner of Rstudio, select the Git tab, select the checkboxes next to all files, and click the Commit button. Write an informative message for the commit, e.g., "Preregistration", again click Commit, and then click the green Push arrow to send your commit to GitHub
5. Go to the GitHub repository for this project, and tag the Commit as a preregistration
6. Optional: Render the preregistration to PDF, and upload it to AsPredicted.org or OSF.io as an attachment
7. Optional: Add study Materials (to which you own the rights) to the repository. It is possible to solicit feedback (by opening a GitHub Issue) and acknowledge outside contributions (by accepting Pull requests)

@@

In this tutorial paper, we have presented a workflow for open reproducible code in science. The workflow aims to lower the threshold for grass-roots adoption of open science principles. It is accompanied by an R-package with convenience functions, and a WORCS project template for Rstudio. This relatively light-weight workflow meets most of the requirements for open science, as detailed in the TOP-guidelines. However, several limitations and issues for future development remain.

@@

Another important challenge is managing collaborations when only the lead author uses Rmarkdown, and the coauthors use Word. In this case, it is possible to Knit the manuscript to Word (.docx), by changing the line `output: papaja::apa6_pdf` in the manuscript's YAML header to `output: papaja::apa6_docx`. There are some limitations to the conversion, discussed [here](https://crsh.github.io/papaja_man/limitations.html#microsoft-word-documents). When soliting feedback from co-authors, ask them to use Tracked Changes and comment bubbles in Word. <!-- LB: The work-around with track-changes in Word files is doable, but not very satisfying. I think you can also use Overleaf instead of Word (user friendly and web based) for bidirectional communication, but haven’t tried this myself. I didn’t know about ‘redoc’, will check it out.-->Then, manually incorporate their changes into the `manuscript.Rmd` file. In most cases, this is the most user-friendly approach, as most lead authors would review changes by co-authors anyway. A second approach is to ask collaborators to work in plain text. In this case, send collaborators the `manuscript.Rmd` file, and ask them to open (and save) it in Word or Notepad as a plain text file. When they send it back, make sure any changes to your local file are committed, and then simply overwrite your local version with their file. In Rstudio, select the file in the Git tab, and click the Diff button to examine what changes the collaborator has made relative to your last committed version. Finally, @peikertReproducibleDataAnalysis2019 mention that the [`redoc` package](https://noamross.github.io/redoc/articles/mixed-workflows-with-redoc.html) [@rossRedocReversibleReproducible2020] might be useful for collaborating with Word users. This package enables bidirectional conversion between Word and Rmarkdown, with support for tracked changes. However, a simpler solution (i.e., asking collaborators to work in plain text) might be sufficient.

@@

WORCS offers a workflow for open reproducible code in science. The step-by-step procedure outlined in this tutorial helps researchers make an entire research project Open and Reproducible. The accompanying R-package provides user-friendly support functions for several steps in the workflow, and an Rstudio project template to get the project set up correctly.

>>>>

abstract: |
  The social sciences are amidst a paradigm shift towards open science. In part,
  this transition has been fueled by cases of scientific fraud and increasing
  awareness of questionable research practices and failed replications. However,
  open science is not
  merely a cure (or punishment) for this crisis - it is also an opportunity.
  Technological advances enable researchers to more easily conduct reliable,
  cumulative, collaborative science. Capitalizing on these advances has the
  potential to accelerate scientific progress. This tutorial paper introduces a
  workflow for open reproducible code in science (WORCS). WORCS is a 
  step-by-step procedure that researchers can follow to make an entire project
  Open and Reproducible. It is based on best practices, and can be used either
  in parallel to, or in absence of, top-down requirements by journals. WORCS
  lowers the threshold for adopting an open science workflow by providing this
  tutorial, along with an R-package with user-friendly support functions, and an
  RStudio project template.

@@

This paper introduces WORCS: A Workflow for Open Reproducible Code in Science. WORCS is a lightweight approach to open science and computational reproducibility. It provides a step-by-step procedure that researchers can follow to make an entire research project Open and Reproducible. WORCS is based on best practices, and can be used either in parallel to, or in absence of, top-down requirements by journals. The main goal of WORCS is to lower the threshold for adopting an open science workflow by providing the present tutorial, along with an R-package with user-friendly support functions, and an RStudio project template.

@@

A recently developed package strikes a great balance between user-friendliness and effectiveness: `renv`, developed by the team behind RStudio. This package maintains a text-based log file of which packages are used, in what versions, and where they were installed from (e.g., CRAN, Bioconductor, GitHub). Being text-based, this log can be version controlled with Git. On a local computer, `renv` installs all packages used in a cache that is shared between all projects that use `renv`. Thus, if one of your projects uses a version of a package that is already in the cache, it does not need to be installed again. This overcomes the limitations of long installation times and large space requirements of `renv`. When someone else loads your project, `renv` will install all of the required packages onto a cache on their computer. Whereas `packrat` copies the source code of all packages, `renv` obtains the packages from their original repositories. Thus, as long as these repositories used maintain their archives, this solution is very lightweight and effective. It is not foolproof, but some have argued that all solutions for computational reproducibility have a limited shelf life [@brownHowLearnedStop2017]. Ultimately, the best solution might be to use a good-enough solution, like `renv`, and acknowledge that all code requires some maintenance if you want to reproduce it in the future.

@@

Working with R is simplified immensely by using the RStudio user interface for R. Many of the tools used in WORCS are embedded directly into the visual user interface of RStudio. RStudio automates and streamlines many tedious or complicated aspects of working with R, Rmarkdown, and Git/GitHub. This makes RStudio a comprehensive solution for open science research projects. Another important feature of RStudio is project management. A project bundles writing, analyses, data, references, etcetera, into a self-contained folder, that can be uploaded entirely to GitHub and downloaded by future users. The `worcs` R-package installs a new RStudio project template. When a new project is initialized from this template, much of the bookkeeping required to set up an open science project is performed automatically.

@@

When using R, software (R packages) can be conveniently cited by calling `citation("packagename")`. This returns an APA-style reference, and a BibTeX entry. However, users of the WORCS project template for RStudio do not need to manually cite R-packages. WORCS generates a template manuscript in APA6 style, based on the `papaja` package [@austPapajaPrepareReproducible2020], which automatically cites all packages used.

@@

Aside from analysis code, the TOP-guidelines also encourage sharing new research materials, and details of the study design and analysis. These goals can be accomplished simply by placing any relevant documents in the RStudio project folder, committing them to the Git repository, and pushing to GitHub. As with any document version controlled in this way, it is advisable to use plain text only.

@@

Several excellent preregistration templates are available in the R-package `prereg` [@austPreregMarkdownTemplates2019], including templates from organizations like [AsPredicted.org](AsPredicted.org) and [OSF.io](OSF.io), and from researchers [e.g., @vantveerPreregistrationSocialPsychology2016]. When opening a new RStudio project with the WORCS project template, it is possible to select one of these preregistration templates, which will generate a file called `preregistration.Rmd`. This file should be used to document study plans, ideally prior to data collection.

@@

1. Create a new Private repository on github, and copy the repository link to the clipboard. The link will look like https://github.com/yourname/yourrepo.git
2. In RStudio, click File > New Project > New directory > WORCS Project Template
    a. Paste the GitHub Repository address in the textbox
    b. Keep the checkbox for `renv` checked if you want to document all dependencies (recommended). The only reason not to do this is if you have dependencies outside of the R environment, or if you are using a more comprehensive solution for computational reproducibility, e.g., @peikertReproducibleDataAnalysis2019.
    c. Select a preregistration template
    d. Click Open in new session, and Create project
3. Write the preregistration `preregistration.Rmd`
4. In the top-right corner of RStudio, select the Git tab, select the checkboxes next to all files, and click the Commit button. Write an informative message for the commit, e.g., "Preregistration", again click Commit, and then click the green Push arrow to send your commit to GitHub
5. Go to the GitHub repository for this project, and tag the Commit as a preregistration
6. Optional: Render the preregistration to PDF, and upload it to AsPredicted.org or OSF.io as an attachment
7. Optional: Add study Materials (to which you own the rights) to the repository. It is possible to solicit feedback (by opening a GitHub Issue) and acknowledge outside contributions (by accepting Pull requests)

@@

In this tutorial paper, we have presented a workflow for open reproducible code in science. The workflow aims to lower the threshold for grass-roots adoption of open science principles. It is accompanied by an R-package with convenience functions, and a WORCS project template for RStudio. This relatively light-weight workflow meets most of the requirements for open science, as detailed in the TOP-guidelines. However, several limitations and issues for future development remain.

@@

Another important challenge is managing collaborations when only the lead author uses Rmarkdown, and the coauthors use Word. In this case, it is possible to Knit the manuscript to Word (.docx), by changing the line `output: papaja::apa6_pdf` in the manuscript's YAML header to `output: papaja::apa6_docx`. There are some limitations to the conversion, discussed [here](https://crsh.github.io/papaja_man/limitations.html#microsoft-word-documents). When soliting feedback from co-authors, ask them to use Tracked Changes and comment bubbles in Word. <!-- LB: The work-around with track-changes in Word files is doable, but not very satisfying. I think you can also use Overleaf instead of Word (user friendly and web based) for bidirectional communication, but haven’t tried this myself. I didn’t know about ‘redoc’, will check it out.-->Then, manually incorporate their changes into the `manuscript.Rmd` file. In most cases, this is the most user-friendly approach, as most lead authors would review changes by co-authors anyway. A second approach is to ask collaborators to work in plain text. In this case, send collaborators the `manuscript.Rmd` file, and ask them to open (and save) it in Word or Notepad as a plain text file. When they send it back, make sure any changes to your local file are committed, and then simply overwrite your local version with their file. In RStudio, select the file in the Git tab, and click the Diff button to examine what changes the collaborator has made relative to your last committed version. Finally, @peikertReproducibleDataAnalysis2019 mention that the [`redoc` package](https://noamross.github.io/redoc/articles/mixed-workflows-with-redoc.html) [@rossRedocReversibleReproducible2020] might be useful for collaborating with Word users. This package enables bidirectional conversion between Word and Rmarkdown, with support for tracked changes. However, a simpler solution (i.e., asking collaborators to work in plain text) might be sufficient.

@@

WORCS offers a workflow for open reproducible code in science. The step-by-step procedure outlined in this tutorial helps researchers make an entire research project Open and Reproducible. The accompanying R-package provides user-friendly support functions for several steps in the workflow, and an RStudio project template to get the project set up correctly.
